Regular singular Volterra equations on complex domains

### 2023-08-22 reg-sing-volterra.tex
Condition sing_tau updated

\item Deal with Condition~\eqref{cond:sing}

@@

\item In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?

@@

\item Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}

@@

  \item Add $\lambda_\text{ratio}$ to Condition~\eqref{cond:diag-basic} as multiplicative constant.

@@

  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSeaGreen}{[No other direct references found.]}

@@

Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.

\par\color{RoyalBlue}Choosing a point $b'$ with $|\zeta(b')| < \delta$ and $q(b') \neq 0$, we can deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p} \zeta\right|\,|\zeta|^{\tau-1}.
\end{align*}
Since Inequality~\ref{eqn:sing-bound} implies that
\begin{align*}
\left|\frac{q(a')}{p(a)}\zeta(a)\right| & \le \tau + C|\zeta(a)| \\
& \le \tau + C\delta
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$, we can conclude that $|\solproto| \lesssim |\zeta|^{\tau-1}$ on the region $|\zeta| < \delta$, as desired.
\end{proof}
\begin{prop}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:slow}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.

@@

Combining the conclusions above, we see that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain = \domain_\text{near} \cup \domain_\text{mid} \cup \domain_\text{far}$, as desired.
\par\color{RoyalBlue}
We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ \textcolor{orange}{[there's no $a'$ here]} (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound

\[   |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
\]

Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$ \textcolor{orange}{[there's no $a'$ here]}. Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.

In particular, 
      \begin{align*}
          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
      \end{align*}
   which is bounded because $|\zeta(a)|>\delta$. \textcolor{orange}{[As Condition~\eqref{cond:slow} is currently stated, $|\zeta| > \delta$ may not be far enough from $\zeta = 0$ to get the $\lambda_p$ and $\lambda_\delta$ bounds. I've strengthened the condition so that $|1/p|$ and $|q/p|$ are at least bounded outside every neighborhood of $\zeta = 0$.]}
\end{proof}
\begin{prop}\label{prop:better-proto-estimate}
Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
\[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
at $\zeta = 0$, where $\epsilon'=\min\{\epsilon, 1\}$.
\end{prop}
\begin{proof}
It's enough to show that
\[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
at $\zeta = 0$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
\begin{align*}
\solproto(a)&=\frac{1}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
& = \frac{1}{p(a)}\,\frac{\zeta(a)^{\tau}}{\zeta(b)^{\tau}}\,\exp\left[-\int_b^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right]\\
& = \zeta(b)^{-\tau}\,\zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right].
\end{align*}
Since $\zeta(b)^{-\tau}$ is a constant, the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want.

@@

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\par\color{RoyalBlue}
Combining the arguments above, we see as desired that
\[ \solproto \in M\zeta^{\tau - 1} + \singexpalg{\tau-1+\lambda'}(\domain), \]
with 
\[ M = \frac{p(b)}{\zeta(b)^{\tau}}\,B^{-1}\,e^{S(b)}. \]
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}

@@

Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$. In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$. In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$. Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough. Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
\subsubsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
\begin{prop}\label{prop:whole-ker-near-bound}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
by keeping $a$ and $a'$ close enough to $\zeta = 0$.
\end{prop}
\begin{proof}
Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
\begin{align*}
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
\end{align*}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.

@@

Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, \textcolor{orange}{[maybe talk about adapting conventions here, since we need that already for the definition of $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to make sense]} and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula

@@

\subsection{Going to the position domain}
By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
\begin{lemma}\label{lem:use-dict}
For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}
\textcolor{orange}{[Where do we explain what $\domain_\alpha$ needs to look like in this example?]}
\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain} replacing the origin $\zeta=0$ with $\zeta=\alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

@@

is bounded as $a,a'$ approach $\zeta=\alpha$.
\begin{verify}
\par Proof of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\color{Tan}
\item \textcolor{orange}{[Condition~\eqref{cond:diag-basic} implies Condition~\eqref{cond:slow}, so we can drop this.]}

@@

Since we're trying to bound $\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$. First, rewrite
\begin{align*}
q(a') & = Q\big(-\zeta(a')\big) \\
& = Q\big(\omega(a, a') - \zeta(a)\big)
\end{align*}
in the form
\[ q(a') = Q_{d-1}\big(\zeta(a)\big)\;\omega(a, a')^{d-1} + \ldots + Q_1\big(\zeta(a)\big)\;\omega(a, a') + Q_0\big(\zeta(a)\big), \]
where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$. We can then write $-\hardker^\alpha(a, a')$ in the form
\[ \frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}, \]
viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$. If we keep $a$ away from the roots of from the roots of $p$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$. It follows that for any $\lambda_\Delta > 0$, we have
\[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
over all $a$ outside a neighborhoood of the roots of $p$ and all $a'$ without restriction.

>>>>

\item \textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}

@@

\item \textcolor{gray}{In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?} \textcolor{MediumSpringGreen}{[Yes.]}
\item Rewrite arguments using new Condition~\eqref{cond:sing}.
\item Show that example satisfies Condition~\eqref{cond:sing}.

@@

\item \textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}

@@

  \item Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.
  \item When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.

@@

  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSpringGreen}{[No other direct references found.]}
\item Set $R_1, \ldots, \ldots R_{d-1}$ to zero.
\item Change definition.
\item Change intro to clarify that our results only apply to some level~1 equations.
\item Change intro to clarify that our results only apply to some level~1 equations.

@@

Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.
\end{proof}
\begin{prop}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}} \textcolor{MediumSpringGreen}{\eqref{cond:slow}}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.

@@

Combining the conclusions above, we see that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain = \domain_\text{near} \cup \domain_\text{mid} \cup \domain_\text{far}$, as desired.
\end{proof}
\begin{prop}\label{prop:better-proto-estimate}
Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
\[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
at $\zeta = 0$, where $\epsilon'=\min\{\epsilon, 1\}$.
\end{prop}
\begin{proof}
It's enough to show that
\[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
at $\zeta = 0$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
\begin{align*}
\solproto(a)&=\frac{1}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
& = \frac{1}{p(a)}\,\frac{\zeta(a)^{\tau}}{\zeta(b)^{\tau}}\,\exp\left[-\int_b^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right]\\
& = \zeta(b)^{-\tau}\,\zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right].
\end{align*}
Since $\zeta(b)^{-\tau}$ is a constant, the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want.

@@

Combining the arguments above, we learn that
\begin{align*}
\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
\end{align*}
at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
\end{proof}
\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}

@@

Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$. In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$. In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$. Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough. Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
\subsubsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$. One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
\begin{prop}\label{prop:whole-ker-near-bound}
Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
by keeping $a$ and $a'$ close enough to $\zeta = 0$.
For the kernel $\hardker$ the claim follows from Condition \eqref{cond:sing}, namely for any $\sigma>\tau$ we can find a neighbourhood of $(0,0)\in\domain^2$ such that 
\[ |\hardker(a, a')| \le \frac{\sigma}{|\zeta(a)|}. \]
\color{RoyalBlue}
Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$. However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrary small margin. Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
&\leq \frac{\tau}{|\zeta(a)|} + C \\
&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
&\le \frac{\tau + C\delta}{|\zeta(a)|}
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
\color{black}

@@

Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}. The Laplace transform of $\varphi$ is defined by the formula

@@

\subsection{Going to the position domain}
By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
\begin{lemma}\label{lem:use-dict}
For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}

\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain} replacing the origin $\zeta=0$ with $\zeta=\alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

@@

is bounded as $a,a'$ approach $\zeta=\alpha$.
\color{black}
\begin{verify}
\par Proof of Ahlfors exercise. First, observe that
\begin{align*}
P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
\end{align*}
Then we see that
\begin{align*}
\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
\frac{1}{P'(-\beta_1)} &= \pi_1
\end{align*}
\end{verify}
\color{Tan}
\item \textcolor{orange}{[Condition~\eqref{cond:diag-basic} implies Condition~\eqref{cond:slow}, so we can drop this.]}

@@

Since we're trying to bound $\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$. First, rewrite
\begin{align*}
q(a') & = Q\big(-\zeta(a')\big) \\
& = Q\big(\omega(a, a') - \zeta(a)\big)
\end{align*}
in the form
\[ q(a') = Q_{d-1}\big(\zeta(a)\big)\;\omega(a, a')^{d-1} + \ldots + Q_1\big(\zeta(a)\big)\;\omega(a, a') + Q_0\big(\zeta(a)\big), \]
where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$. We can then write $-\hardker^\alpha(a, a')$ in the form
\[ \frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}, \]
viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$. If we keep $a$ away from the roots of from the roots of $p$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$. It follows that for any $\lambda_\Delta > 0$, we have
\[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
over all $a$ outside a neighborhood of the roots of $p$ and all $a'$ without restriction.
